HPC--101\\Onboarding

### 2023-05-06 hpc_101/sections/09_appendix.tex
small corrections

\end{frame}
\section{Monitoring Jobs and Partitions}{Monitoring Jobs and Partitions}
\begin{frame}[fragile]
\frametitle{Monitoring Running Jobs}
\begin{block}{\textbf{squeue}}
\begin{semiverbatim}\tiny \texttt
[victorgc@node-0093 HDM]\$ squeue --me
             JOBID PARTITION     NAME     USER ST       TIME  NODES NODELIST(REASON)
          43486015   sandbox     bash victorgc  R    2:05:37      1 node-0093
\end{semiverbatim}
\end{block}
The --me flag can be removed and \textbf{squeue} will report all running jobs in the system.
\begin{block}{\textbf{squeue}}
\begin{semiverbatim}\tiny \texttt
[victorgc@node-0093 HDM]\$ squeue | head
             JOBID PARTITION     NAME     USER ST       TIME  NODES NODELIST(REASON)
          43078226   bioinfo    sgSQL     user  R 23-02:12:35      1 node-0327
          43078227   bioinfo cromwell     user  R 23-02:12:09      1 node-0327
          43485890   bioinfo       QC     user  R    4:45:59      1 node-0327
          43399271   bioinfo      TQC     user  R 3-20:49:10      1 node-0328
          43485868 exclusive    MoSe2     user  R    5:20:14      1 node-0296
          43485867 exclusive    MoSe2     user  R    5:30:46      1 node-0295
          43485866 exclusive    MoSe2     user  R    5:35:43      1 node-0294
          43485815 exclusive    MoSe2     user  R    5:57:03      1 node-0281
\end{semiverbatim}
\end{block}
\numlessfootnotetxt{\tiny \href{https://slurm.schedmd.com/squeue.html}{https://slurm.schedmd.com/squeue.html}}

>>>>

\end{frame}
\section[Monitoring Jobs and Partitions]{Monitoring Jobs and Partitions}
\begin{frame}[fragile]
\frametitle{Monitoring Running Jobs}
\begin{block}{\textbf{squeue}}
\begin{semiverbatim}\tiny \texttt
[victorgc@node-0093 HDM]\$ squeue -u victorgc
             JOBID PARTITION     NAME     USER ST       TIME  NODES NODELIST(REASON)
          43486015   sandbox     bash victorgc  R    2:05:37      1 node-0093
\end{semiverbatim}
\end{block}
By default, \textbf{squeue} will report all running jobs in the system.
\begin{block}{\textbf{squeue}}
\begin{semiverbatim}\tiny \texttt
[victorgc@node-0093 HDM]\$ squeue | head
             JOBID PARTITION     NAME     USER ST       TIME  NODES NODELIST(REASON)
          43078226   bioinfo    sgSQL     user  R 23-02:12:35      1 node-0327
          43078227   bioinfo cromwell     user  R 23-02:12:09      1 node-0327
          43485890   bioinfo       QC     user  R    4:45:59      1 node-0327
          43399271   bioinfo      TQC     user  R 3-20:49:10      1 node-0328
          43485868 exclusive    MoSe2     user  R    5:20:14      1 node-0296
          43485867 exclusive    MoSe2     user  R    5:30:46      1 node-0295
          43485866 exclusive    MoSe2     user  R    5:35:43      1 node-0294
          43485815 exclusive    MoSe2     user  R    5:57:03      1 node-0281
\end{semiverbatim}
\end{block}
\numlessfootnotetxt{\tiny \href{https://slurm.schedmd.com/squeue.html}{https://slurm.schedmd.com/squeue.html}}
